\chapter{\label{cha:Preface}Preface}
Dear reader,

The last nine months have been a challenging but incredible journey. I was not well acquainted with the subject of the thesis, so I was continuously pushed further and further away from my comfort zone as the project progressed. While this has been a very educational and rewarding journey, it would not have been possible without the help of many wonderful people.

First and foremost, I would like to thank Anand Ashok Sawant, who introduced me to this topic and whose insights were invaluable to the project. Many thanks to Toufique Ahmed for always being available to discuss difficulties and answering my many questions. Thanks to Prof. Arie van Deursen for introducing me to the topic and the right people, for the many valuable insights and for keeping the project on track. Thanks to Maliheh Izadi for sharing her extensive knowledge on the topic, for always being available for questions and her help writing the thesis. Many thanks to Prof. Prem Devanbu for always providing profound insights and his academic curiosity during the weekly meetings. Also, I would like to thank the DECAL lab members, and specifically Toufique, Prem and Anand, for their hospitality during my visit to Davis.

I would also like to thank my friends and colleagues at Eye Security for their continued support and the Friday evening hacking sessions, which were a welcome distraction. Finally, I thank my friends and family for always being there for me and supporting me throughout this journey.
\vskip1cm
\begin{flushright}
\theauthor\\
Delft, the Netherlands \\
\today\\
\end{flushright}